Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-02-27 article.qmd
Use vector file for figure 6

![Performance of different softwares to solve models from the curated section of BioModels. (left) Run time for the model BIOMD3 as a function of the number of output points. (right) Run time for different models for 300 output points, using the geometric mean of the different softwares to order them.](src/performance/figures/performance.png){#fig-runtime}

>>>>

![Performance of different softwares to solve models from the curated section of BioModels. (left) Run time for the model BIOMD3 as a function of the number of output points. (right) Run time for different models for 300 output points, using the geometric mean of the different softwares to order them.](src/performance/figures/performance.svg){#fig-runtime}
